---
output: github_document
bibliography: "references.bib"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(knitr)
```

# macrogrow

# Introduction

This package intends to formalise and disseminate the macroalgae growth model originally developed by @hadley_modeling_2015 and modified in subsequent works. 

# Getting started

Install the package with:

```{r eval=F, include=T}
devtools::install_github("https://github.com/stormeyseas/macrogrow.git")
```

The main function to grow macroaglae is `grow_macroalgae()`. A simple case is shown below, and you can find a full use case in the [Grow macroalgae](vignettes/grow-macroalgae.Rmd) article.

The model requires three basic sets of data to run:

* daily input vectors of temperature, surface irradience, salinity, and water velocity, 
* a named vector of species-specific parameters, and
* a named vector of site-specific parameters


<!-- # Updates and changes -->

# References
