---
output: github_document
bibliography: "references.bib"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(knitr)
```

# macrogrow

# Introduction

This package intends to formalise and disseminate the macroalgae growth model originally developed by @hadley_modeling_2015 and modified in subsequent works. 

# Usage

Install the package with:

```{r eval = FALSE}
devtools::install_github("https://github.com/stormeyseas/macrogrow.git")
```

The model requires daily input vectors of temperature, surface irradience, salinity, and water velocity, along with a named vector of species-specific parameters to run. You can find a full use case in the [Grow macroalgae](vignettes/grow-macroalgae.Rmd) article, and a template for the required species parameters has been included within the package as asparagopsis_armata.csv. 

<!-- # Updates and changes  -->

# References
