---
output: github_document
bibliography: "references.bib"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(knitr)
```

# macrogrow

This package intends to formalise and disseminate the macroalgae growth model originally developed by @hadley_modeling_2015 and modified in subsequent works. 

## Getting started 

Install the package with:

```{r eval=F, include=T}
devtools::install_github("https://github.com/stormeyseas/macrogrow")
```

## Grow macroalgae 

The main function to grow macroaglae is `grow_macroalgae()`. You can find a full use case in the [Grow macroalgae](vignettes/grow-macroalgae.Rmd) article. 

The model requires three basic sets of data to run:

* daily input vectors of environmental input drivers
  * Essential: temperature, nitrate, ammonium
  * Optional: surface irradience, salinity, water velocity
* a named vector of species-specific parameters, and
* a named vector of site-specific parameters

The package includes default datasets for each of these so that a simple example run can be executed immediately. These datasets are called:

* env
* a_armata (_Asparagopsis armata_ parameters, see <paper DOI to go here> for details)
* site_params

Most other functions included here are called within `grow_macroalgae()`. There is also a checking function `check_macroalgae()` which is designed to take all the same parameters as `grow_macroalgae()` and output a report on their validity. This is to reduce the error handling contained within `grow_macroalgae()` and its helper functions. As a consequence, `grow_macroalgae()` will likely give very unhelpful errors. 

## References
