---
title: "Grow macroalgae"
author: "Tormey Reimer"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
---

This space will be used to detail how to use the main model function, `grow_macroalgae()`.

```{r setup}
library(macrogrow)
library(magrittr)
library(units)
library(lubridate)
library(ggplot2)
library(cowplot)
```

# Load datasets

Within this package, there are three default datasets:

* `env` is a datafrae of default environmental variables
* `a_armata` is a named vector of parameters for _Asparagopsis armata_
* `site_params` is a named vector of site-specific parameters (culture conditions)

## Check environmental data

First let's check to make sure our environmental inputs look reasonable. You should also check that they are within the species tolerance limits or the macroalgae will not grow (or maybe that's what you want).

```{r env-plots, fig.width=10, fig.height=12}
p_temperature <- ggplot(env, aes(x = t, y = temperature)) +
     geom_line(linewidth = 0.75) +
     theme_classic() +
     labs(x = "Day of year", y = "Temperature (°C)") +
     ggtitle("Surface temperature")

p_light <- ggplot(env, aes(x = t, y = (light*exp(-(kW*site_params['d_top']))))) +
     geom_line(linewidth = 0.75) +
     theme_classic() +
     labs(x = "Day of year", y = "Light at canopy top (μmol m⁻² s⁻¹)") +
     ggtitle("Light at top of canopy")

p_salinity <- ggplot(env, aes(x = t, y = salinity)) +
     geom_line(linewidth = 0.75) +
     theme_classic() +
     labs(x = "Day of year", y = "Salinity (g L⁻¹)") +
     ggtitle("Salinity")

p_velocity <- ggplot(env, aes(x = t, y = velocity)) +
     geom_line(linewidth = 0.75) +   
     theme_classic() +
     labs(x = "Day of year", y = "Velocity (m s⁻¹)") +
     ggtitle("Water Velocity")

p_nitrate <- ggplot(env, aes(x = t, y = nitrate)) +
     geom_line(linewidth = 0.75) +   
     theme_classic() +
     labs(x = "Day of year", y = "Nitrate (mg m⁻³)") +
     ggtitle("Ambient nitrate concentration")

p_ammonium <- ggplot(env, aes(x = t, y = ammonium)) +
     geom_line(linewidth = 0.75) +   
     theme_classic() +
     labs(x = "Day of year", y = "Ammonium (mg m⁻³)") +
     ggtitle("Ambient ammonium concentration")

plot_grid(
     p_temperature, p_light, p_salinity, p_velocity, p_nitrate, p_ammonium,
     ncol = 2
)
```

# Get initial macroalgae stat

Three values are required for macroalgae initialisation: $N_f$, $N_s$, and $Q_{rel}$. $N_f$, $N_s$ must be in mg m$^{-3}$ and can be calculated from an initial biomass using `biomass_to_Nf()`.

```{r initial-state}

init_biomass <- 0.005 %>% set_units("g L-1") %>% set_units("mg m-3") %>% drop_units()

init_NfNs <- biomass_to_Nf(
     biomass = init_biomass, 
     Q_rel = 0.5, 
     spec_params = a_armata,
     dry = T
)

init_state <- c(init_NfNs, Q_rel = 0.5)
```

# Check all inputs

Since the `grow_macroalgae()` function has so many inputs with very specific requirements, the `check_grow()` function is designed to take the exact same inputs as `grow_macroalgae()` and provide a report.

```{r check for macrogrow 1, echo=T}
check_grow(
    t = 1:60,
    temperature = env$temperature[1:60],
    salinity = env$salinity[1:60],
    light = env$light[1:60],
    kW = env$kW[1:60],
    velocity = env$velocity[1:60],
    nitrate = env$nitrate[1:60],
    ammonium = env$ammonium[1:60],
    ni_uptake = NA,
    am_uptake = NA,
    site_params = site_params,
    spec_params = a_armata,
    initials = init_state,
    sparse_output = T,
    other_constants = c(s = 0.0045, gam = 1.13, a2 = 0.2^2, Cb = 0.0025)
  )
```

# Grow macroalgae 

```{r grow macroalgae, eval=F}
gro <- grow_macroalgae(
    t = 1:60,
    temperature = env$temperature[1:60],
    salinity = env$salinity[1:60],
    light = env$light[1:60],
    kW = env$kW[1:60],
    velocity = env$velocity[1:60],
    nitrate = env$nitrate[1:60],
    ammonium = env$ammonium[1:60],
    ni_uptake = NA,
    am_uptake = NA,
    site_params = site_params,
    spec_params = a_armata,
    initials = init_state,
    sparse_output = T,
    other_constants = c(s = 0.0045, gam = 1.13, a2 = 0.2^2, Cb = 0.0025)
  )
```


