---
title: "Grow macroalgae"
author: "Tormey Reimer"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
---

This space will be used to detail how to use the main model function, `grow_macroalgae()`.

```{r setup}
library(macrogrow)
library(magrittr)
library(units)
library(lubridate)
library(ggplot2)
library(cowplot)
```

# Load datasets

Within this package, there are three default datasets:

* `env` is a datafrae of default environmental variables
* `a_armata` is a named vector of parameters for _Asparagopsis armata_
* `site_params` is a named vector of site-specific parameters (culture conditions)

## Check environmental data

First let's check to make sure our environmental inputs look reasonable. We should also check that they are within the species tolerance limits or the macroalgae will not grow.

```{r env-plots, fig.width=10, fig.height=12}
p_temperature <- ggplot(env, aes(x = t, y = temperature)) +
     geom_line(linewidth = 0.75) +
     geom_hline(yintercept = a_armata["T_opt"], linewidth = 1) +
     geom_hline(yintercept = a_armata["T_min"], linewidth = 0.75, linetype = "dashed") +
     geom_hline(yintercept = a_armata["T_max"], linewidth = 0.75, linetype = "dashed") +     
     theme_classic() +
     labs(x = "Day of year", y = "Temperature (°C)") +
     ggtitle("Temperature")

p_light <- ggplot(env, aes(x = t, y = (light*exp(-(kW*site_params['d_top']))))) +
     geom_line(linewidth = 0.75) +
     geom_hline(yintercept = a_armata["I_o"], linewidth = 0.75, linetype = "dashed") + 
     theme_classic() +
     labs(x = "Day of year", y = "Light at canopy top (μmol m⁻² s⁻¹)") +
     ggtitle("Light")

p_salinity <- ggplot(env, aes(x = t, y = salinity)) +
     geom_line(linewidth = 0.75) +
     geom_hline(yintercept = a_armata["S_opt"], linewidth = 1) +
     geom_hline(yintercept = a_armata["S_min"], linewidth = 0.75, linetype = "dashed") +
     geom_hline(yintercept = a_armata["S_max"], linewidth = 0.75, linetype = "dashed") +     
     theme_classic() +
     labs(x = "Day of year", y = "Salinity (g L⁻¹)") +
     ggtitle("Salinity")

p_velocity <- ggplot(env, aes(x = t, y = velocity)) +
     geom_line(linewidth = 0.75) +   
     theme_classic() +
     labs(x = "Day of year", y = "Velocity (m s⁻¹)") +
     ggtitle("Water Velocity")

p_nitrate <- ggplot(env, aes(x = t, y = nitrate)) +
     geom_line(linewidth = 0.75) +   
     theme_classic() +
     labs(x = "Day of year", y = "Nitrate (mg m⁻³)") +
     ggtitle("Nitrate Concentration")

p_ammonium <- ggplot(env, aes(x = t, y = ammonium)) +
     geom_line(linewidth = 0.75) +   
     theme_classic() +
     labs(x = "Day of year", y = "Ammonium (mg m⁻³)") +
     ggtitle("Ammonium Concentration")

plot_grid(
     p_temperature, p_light, p_salinity, p_velocity, p_nitrate, p_ammonium,
     cols = 2
)
```

# Check all inputs

Since the `grow_macroalgae()` function has so many inputs with very specific requirements, the `check_grow()` function is designed to take the exact same inputs as `grow_macroalgae()` and provide a report.

```{r check for macrogrow, eval=F}
check_grow(
  start = start,
  grow_days = grow_days,
  temperature = env$temperature[gd],
  salinity = env$salinity[gd],
  light = env$light[gd],
  # kW = env$kW[gd],
  velocity = env$velocity[gd],
  nitrate = env$nitrate[gd],
  ammonium = env$ammonium[gd],
  ni_uptake = "linear",
  am_uptake = "MM",
  site_params = site_params, 
  spec_params = a_armata,
  initials = init_arma
)
```

# Grow macroalgae 

```{r grow macroalgae, eval=F}
gro <- grow_macroalgae(
  start = start,
  grow_days = grow_days,
  temperature = env$temperature[gd],
  salinity = env$salinity[gd],
  light = env$light[gd],
  kW = env$kW[gd],
  velocity = env$velocity[gd],
  nitrate = env$nitrate[gd],
  ammonium = env$ammonium[gd],
  ni_uptake = "linear",
  am_uptake = "MM",
  site_params = site_params, 
  spec_params = a_armata,
  initials = init_arma
)
```


