---
title: "Forcing functions"
output: html_document
bibliography: /resources/bibliography.bib 
execute:
  eval: false
---

```{r setup}
#| include: false

# install.packages("pacman")

# Special, not on CRAN
# devtools::install_github("pecanproject/pecan/modules/data.atmosphere")

packs <- c("knitr", "tidyverse", "tidymodels", "arrow"
           # , "MASS", "car", "gamlss", "fitdistrplus", "statmod", "stats", "tweedie", "geosphere", "ggmap", "scales", "kableExtra", "multcomp", "insight", "ggeffects", "plotrix", "Rmisc", "BSagri", "magick",  "nlstools", "EnvStats"
           )

pacman::p_load(char = packs)

# Outdated, possibly not in use any more
# p_load("nlstimedist")
```

Axis labels, etc.

```{r globals}
irr_lab <-
  bquote('Log of irradience (' * mu * 'mol photons ' ~ m ^ -2 ~ s ^ -1 * ')')
lab_N <- bquote("Concentration ("*mu*"mol N "~L^-1*")")
lab_N <- bquote("Concentration ("*mu*"mol N "~L^-1*")")
lab_amm.log <- bquote("Log of concentration ("*mu*"mol "~NH[4]*")")
lab_nit <- bquote("Concentration ("*mu*"mol "~NO[3]*")")
temp_lab <- expression(Temperature ~ (degree * C))
t <- data.frame(as.numeric(1:(365 + 30)))
colnames(t) <- c("day_t")

nice <- theme_classic() + 
  theme(legend.position = "none") + theme(text = element_text(size = 12, family = "sans", colour = "black"))
prettybars <- scale_fill_brewer(palette = "Set1")
```

# Light and temperature

## Environmental data

This loads all the environmental data from WP1 and WP2 (all_CRC), as well as data from the BOM.

```{r load and clean BOM data}
solar_BOM <- list(
  read.csv("data-raw/IDCJAC0016_094020_2021_Data.csv", sep = ','),
  read.csv("data-raw/IDCJAC0016_092157_2021_Data.csv", sep = ',')
)
colnames(solar_BOM[[1]]) <- colnames(solar_BOM[[2]]) <- c("Product.code", "BOM.station.number", "Year", "Month", "Day", "DOY", "Daily.solar.exp.MJmm")

solar_BOM <- bind_rows(solar_BOM)

solar_BOM <- solar_BOM %>% 
  mutate(I_ppfd = solarMJ2ppfd(Daily.solar.exp.MJmm),
         Product.code = as.factor(Product.code),
         BOM.station.number = as.factor(BOM.station.number),
         site = case_when(BOM.station.number == "94020" ~ "Dover",
                          BOM.station.number == "92157" ~ "Triabunna"),
         site = as.factor(site),
         date = make_date(y = Year, m = Month, d = Day)) %>% 
  dplyr::select(-c(Year, Month, Day))

temp_BOM <- list(
  read.csv("data-raw/IDCJAC0011_094020_2021_Data.csv", sep = ',') %>% 
    mutate(measure = "minimum"),
  read.csv("data-raw/IDCJAC0010_094020_2021_Data.csv", sep = ',') %>% 
    mutate(measure = "maximum")
)
colnames(temp_BOM[[1]]) <- colnames(temp_BOM[[2]]) <- c("Product.code", "BOM.station.number", "Year", "Month", "Day", "DOY", "temperature.C", "Days.of.accumulation", "Quality", "measure")

temp_BOM <- bind_rows(temp_BOM) 

temp_BOM <- temp_BOM %>% 
  mutate(measure = as.factor(measure),
         Product.code = as.factor(Product.code),
         BOM.station.number = as.factor(BOM.station.number),
         Quality = as.factor(Quality),
         site = case_when(BOM.station.number == "94020" ~ "Dover",
                          BOM.station.number == "92157" ~ "Triabunna"),
         site = as.factor(site),
         date = make_date(y = Year, m = Month, d = Day)) %>% 
  dplyr::select(-c(Year, Month, Day))
```

```{r load and inspect crcp light data}
all_CRC <- read.csv("data-raw/all_env_data.csv", sep = ',')

all_CRC <- all_CRC %>%
  mutate(site = factor(site, levels = c("Oakhampton", "Tower Bay"), labels = c("Okehampton", "Tower Bay")),
         depth_m = as.factor(depth_m),
         date_time = as_datetime(date_time, format = "%d/%m/%Y %H:%M:%S"),
         date = dmy(date))

solar_CRC <- all_CRC %>% 
  dplyr::select(-temp_C)

plot(solar_CRC$day_t, solar_CRC$I_ppfd) 
# There are three points where I_ppfd seems to have maxed out (?) at ~25000, clear outliers
solar_CRC$I_ppfd[solar_CRC$I_ppfd > 20000] <- NA
# Only interested in daytime (>0) light
solar_CRC$I_ppfd[solar_CRC$I_ppfd == 0] <- NA

plot(solar_CRC$day_t, solar_CRC$I_ppfd)
```

```{r inspect CRCP temperature data}
temp_CRC <- all_CRC %>% 
  dplyr::select(-I_lux, -I_ppfd) %>% 
  mutate(daynight = case_when(hour(date_time) >= 7 & hour(date_time) < 19 ~ "day",
                              TRUE ~ "night"))

plot(temp_CRC$day_t, temp_CRC$temp_C) 
# No obvious outliers, just a few very cold days (normal for Tassie)
```

```{r daily means}
# Irradience
solar_CRC_means <- solar_CRC %>%
  group_by(site, depth_m, day_t) %>%
  reframe(daynight = "day",
          I_mean = mean(I_ppfd, na.rm = T),
          I_sd = sd(I_ppfd, na.rm = T),
          n = n())

ggplot(solar_CRC_means, 
       aes(x = day_t, y = I_mean, color = depth_m, shape = site)) +
  geom_point() +
  ggtitle("Mean daily irradience, CRCP data")

solar_BOM_means <- solar_BOM %>% 
  group_by(site, DOY) %>% 
  reframe(depth_m = "0",
          day_t = DOY,
          daynight = "day",
          I_mean = mean(I_ppfd, na.rm = T),
          I_sd = sd(I_ppfd, na.rm = T),
          n = n()) %>% 
  dplyr::select(-DOY)

ggplot(solar_BOM_means, 
       aes(x = day_t, y = I_mean, colour = site)) +
  geom_point() +
  ggtitle("Mean daily irradience, BOM data")

# Temperature
temp_CRC_means <- temp_CRC %>%
  group_by(site, depth_m, day_t, daynight) %>%
  reframe(T_mean = mean(temp_C, na.rm = T),
          T_sd = sd(temp_C, na.rm = T),
          n = n())

ggplot(temp_CRC_means, 
       aes(x = day_t, y = T_mean, color = interaction(depth_m, daynight), shape = site)) +
  geom_point() +
  ggtitle("Mean daily temperature, CRCP data")

temp_BOM_means <- temp_BOM %>% 
  group_by(site, DOY, measure) %>% 
  reframe(depth_m = "0",
          day_t = DOY,
          daynight = "day",
          T_mean = mean(temperature.C, na.rm = T),
          T_sd = sd(temperature.C, na.rm = T),
          n = n()) %>% 
  dplyr::select(-DOY)

levels(temp_BOM_means$measure) <- c("mean_max", "mean_min")

ggplot(temp_BOM_means, 
       aes(x = day_t, y = T_mean, colour = interaction(site, measure))) +
  geom_point() +
  ggtitle("Mean daily min and max temperature, BOM data")
```


```{r combine all data}
solar_means <- list(
  solar_CRC_means %>% mutate(source = "CRC"),
  solar_BOM_means %>% mutate(source = "BOM")
)

solar_means <- bind_rows(solar_means) %>% 
  mutate(source = as.factor(source),
         daynight = factor(daynight, levels = "day", "night"),
         depth_m = as.factor(depth_m))

# write_parquet(solar_means, sink = tempfile(pattern = "solar_means", fileext = ".parquet", tmpdir = "D:/R_temp_files/NR-model-package/data"))

temp_means <- list(
  temp_CRC_means %>% mutate(source = "CRC"),
  temp_BOM_means %>% mutate(source = "BOM")
)

temp_means <- bind_rows(temp_means) %>% 
  mutate(source = as.factor(source),
         daynight = as.factor(daynight),
         depth_m = as.factor(depth_m))

# write_parquet(temp_means, sink = tempfile(pattern = "temp_means", fileext = ".parquet", tmpdir = "D:/R_temp_files/NR-model-package/data"))
```

# Initial plotting

```{r initial I plot}
(p_I <- ggplot(solar_means, 
               aes(x = day_t, y = I_mean, shape = site, color = depth_m, size = source)) +
  geom_point() +
  scale_color_manual(values = c("0" = "grey", "2" = "orange", "5" = "steelblue")) +
  scale_size_manual(values = c("BOM" = 1.5, "CRC" = 2.5)) +
  scale_shape_manual(values = c("Dover" = 1, "Triabunna" = 1, "Okehampton" = 0, "Tower Bay" = 2)) +
  theme_classic())
```

```{r initial T plot}
(p_T <- ggplot(filter(temp_means, is.na(measure) | measure == "mean_max")) +
   geom_point(aes(x = day_t, y = T_mean, shape = site, color = depth_m, size = source)) +
   scale_color_manual(values = c("surf" = "grey", "2" = "orange", "5" = "steelblue")) +
   scale_size_manual(values = c("BOM" = 1.5, "CRC" = 2.5)) +
   scale_shape_manual(values = c("Dover" = 1, "Triabunna" = 1, "Okehampton" = 0, "Tower Bay" = 2)) +
   theme_classic())
```

# Fitting functions to data

## Temperature

There is only Dover for BOM temperature, and the mean maximum is a much closer fit to the CRCP data. However, basically the only point of the BOM data is to fill in the gaps where the CRC wasn't collecting data.

```{r nls on BOM temp}
# Based on CRCP and BOM data (max only)
xT <- as.formula(T_mean ~ a + sin((2 * pi * (day_t + b) + pi / 2) / 365) * c)
yT <- nls(xT, start = list(a = 15, b = 60, c = 2), 
           data = filter(temp_means, is.na(measure) | measure == "mean_max"))
# summary(yT)
aT <- coef(summary(yT))[1]
bT <- round(coef(summary(yT))[2], 0)
cT <- coef(summary(yT))[3]

# Based on CRCP data only
yT1 <- nls(xT, start = list(a = 15, b = 60, c = 2), data = filter(temp_means, is.na(measure)))
# summary(yT1)
aT1 <- coef(summary(yT1))[1]
bT1 <- round(coef(summary(yT1))[2], 0)
cT1 <- coef(summary(yT1))[3]

# Based on CRCP data or BOM data, depending on whether CRCP data is available
ydata <- temp_means %>%
  filter(measure == "mean_max" | is.na(measure)) %>% 
  dplyr::select(-measure, -n, -T_sd) %>% 
  pivot_wider(names_from = c(source, site, daynight, depth_m), values_from = T_mean)

ydata <- ydata %>% 
  mutate(T_mean_2 = case_when(
    !is.na(CRC_Okehampton_day_2) | !is.na(`CRC_Tower Bay_day_2`) | !is.na(`CRC_Tower Bay_night_2`) ~ 
      mean(c(CRC_Okehampton_day_2, `CRC_Tower Bay_day_2`, `CRC_Tower Bay_night_2`), na.rm = T),
    TRUE ~ BOM_Dover_day_0),
         T_mean_5 = case_when(
    !is.na(`CRC_Tower Bay_day_5`) | !is.na(`CRC_Tower Bay_night_5`) ~ 
      mean(c(`CRC_Tower Bay_day_2`, `CRC_Tower Bay_night_2`), na.rm = T),
    TRUE ~ BOM_Dover_day_0))

xT2 <- as.formula(T_mean_2 ~ a + sin((2 * pi * (day_t + b) + pi / 2) / 365) * c)
yT2 <- nls(xT2, start = list(a = 15, b = 60, c = 2), data = ydata)
# summary(yT2)
aT2 <- coef(summary(yT2))[1]
bT2 <- round(coef(summary(yT2))[2], 0)
cT2 <- coef(summary(yT2))[3]

xT5 <- as.formula(T_mean_5 ~ a + sin((2 * pi * (day_t + b) + pi / 2) / 365) * c)
yT5 <- nls(xT5, start = list(a = 15, b = 60, c = 2), data = ydata)
# summary(yT5)
aT5 <- coef(summary(yT5))[1]
bT5 <- round(coef(summary(yT5))[2], 0)
cT5 <- coef(summary(yT5))[3]

xT <- 1:365
ydata <- data.frame(x = xT) %>% 
  mutate(yT = aT + sin((2 * pi * (x + bT) + pi / 2) / 365) * cT,
         yT1 = aT1 + sin((2 * pi * (x + bT1) + pi / 2) / 365) * cT1,
         yT2 = aT2 + sin((2 * pi * (x + bT2) + pi / 2) / 365) * cT2,
         yT5 = aT5 + sin((2 * pi * (x + bT5) + pi / 2) / 365) * cT5)
```

I've chosen the BOM + CRCP method.

```{r chosen}
summary(yT)

p_T + 
  geom_line(data = ydata, aes(x = x, y = yT), linetype = "dashed") +
  geom_line(data = ydata, aes(x = x, y = yT1), linetype = "solid") #+
  # geom_line(data = ydata, aes(x = x, y = yT2),  linetype = "solid", color = "orange") +
  # geom_line(data = ydata, aes(x = x, y = yT5), linetype = "solid", color = "steelblue")
```

## Irradience

Below I seemed to be using a lot of trial and error so I thought I would do it somewhat properly.

```{r nls on BOM ppfd}
xI <- as.formula(I_mean ~ aI + sin((2 * pi * (day_t + bI) + pi / 2) / 365) * cI)

yI_Dov <- nls(xI, start = list(aI = 850, bI = 60, cI = 600), 
              data = filter(solar_means, source == "BOM" & site == "Dover"))
summary(yI_Dov)
a_Dov <- coef(summary(yI_Dov))[1]
b_Dov <- round(coef(summary(yI_Dov))[2],0)
c_Dov <- coef(summary(yI_Dov))[3]

yI_Tri <- nls(xI, start = list(aI = 850, bI = 60, cI = 600), 
              data = filter(solar_means, source == "BOM" & site == "Triabunna"))
summary(yI_Tri)
a_Tri <- coef(summary(yI_Tri))[1]
b_Tri <- round(coef(summary(yI_Tri))[2],0)
c_Tri <- coef(summary(yI_Tri))[3]

yI_BOM <- as.data.frame(xT) %>%
  mutate(Dover = a_Dov + sin((2 * pi * (xT + b_Dov) + pi / 2) / 365) * c_Dov,
         Triabunna = a_Tri + sin((2 * pi * (xT + b_Tri) + pi / 2) / 365) * c_Tri) %>% 
  pivot_longer(names_to = "site", values_to = "I_mean", cols = c(Dover, Triabunna)) %>% 
  mutate(depth_m = "0",
         source = "BOM")

p_I + 
  geom_line(data = yI_BOM, aes(x = xT, y = I_mean), linetype = "solid") +
  geom_line(data = yI_BOM, aes(x = xT, y = I_mean), linetype = "dashed")
```

The existing coefficients stay the same as the BOM plot, and now I'm just adjusting the kW.I'm going to go with the Triabunna irradience, but they're basically the same.

```{r adapting for CRC ppfd}
xI.2m <- as.formula(I_ppfd ~ (aI.Tri + sin((2 * pi * (day_t + bI.Tri) + pi / 2) / 365) * cI.Tri) * exp(-kW.2 * 2))
y.I.2m <- nls(xI.2m,
              start = list(kW.2 = 0.6),
              data = filter(env.CRC, depth_m == "2"))
summary(y.I.2m)
kW.2 <- coef(summary(y.I.2m))[1]

xI.5m <- as.formula(I_ppfd ~ (aI.Tri + sin((2 * pi * (day_t + bI.Tri) + pi / 2) / 365) * cI.Tri) * exp(-kW.5 * 5))
y.I.5m <- nls(xI.5m,   
              start = list(kW.5 = 0.6),
              data = filter(env.CRC, depth_m == "5"))
summary(y.I.5m)
kW.5 <- coef(summary(y.I.5m))[1]

kW.mean <- (kW.2 + kW.5)/2
kW.other <- 0.85

m2.Kw2 <- t %>% 
  mutate(depth = as.factor("2m"),
         kW.used = as.factor("2m"),
         val = (aI.Tri + sin((2 * pi * (day_t + bI.Tri) + pi / 2) / 365) * cI.Tri) * exp(-kW.2 * 2))
m2.Kw5 <- t %>%
  mutate(depth = as.factor("2m"),
         kW.used = as.factor("5m"),
         val = (aI.Tri + sin((2 * pi * (day_t + bI.Tri) + pi / 2) / 365) * cI.Tri) * exp(-kW.5 * 2))
m2.KwM <- t %>%
  mutate(depth = as.factor("2m"),
         kW.used = as.factor("mean"),
         val = (aI.Tri + sin((2 * pi * (day_t + bI.Tri) + pi / 2) / 365) * cI.Tri) * exp(-kW.mean * 2))
m5.Kw2 <- t %>%
  mutate(depth = as.factor("5m"),
         kW.used = as.factor("2m"),
         val = (aI.Tri + sin((2 * pi * (day_t + bI.Tri) + pi / 2) / 365) * cI.Tri) * exp(-kW.2 * 5))
m5.Kw5 <- t %>%
  mutate(depth = as.factor("5m"),
         kW.used = as.factor("5m"),
         val = (aI.Tri + sin((2 * pi * (day_t + bI.Tri) + pi / 2) / 365) * cI.Tri) * exp(-kW.5 * 5))
m5.KwM <- t %>%
  mutate(depth = as.factor("5m"),
         kW.used = as.factor("mean"),
         val = (aI.Tri + sin((2 * pi * (day_t + bI.Tri) + pi / 2) / 365) * cI.Tri) * exp(-kW.mean * 5))
m2.KwO <- t %>%
  mutate(depth = as.factor("2m"),
         kW.used = as.factor("other"),
         val = (aI.Tri + sin((2 * pi * (day_t + bI.Tri) + pi / 2) / 365) * cI.Tri) * exp(-kW.other * 2))
m5.KwO <- t %>%
  mutate(depth = as.factor("5m"),
         kW.used = as.factor("other"),
         val = (aI.Tri + sin((2 * pi * (day_t + bI.Tri) + pi / 2) / 365) * cI.Tri) * exp(-kW.other * 5))

y.I.CRC <- as.data.frame(rbind(m2.Kw2, m2.Kw5, m2.KwM, m5.Kw2, m5.Kw5, m5.KwM, m2.KwO, m5.KwO))

p_I + 
  geom_line(data = y.I.CRC, 
            aes(x = day_t, y = val, color = kW.used, linetype = depth)) +
  scale_color_manual(values = c("2m" = "orange", "5m" = "steelblue", "mean" = "black", "other" = "red"))+
  scale_linetype_manual(values = c("2m" = "solid", "5m" = "dashed"))

rm(m2.Kw2, m2.Kw5, m2.KwM, m5.Kw2, m5.Kw5, m5.KwM, m2.KwO, m5.KwO)
```

## Plots

```{r final I plot}
(p.Irr <- ggplot() +
   geom_point(data = data.env, aes(x = day_t, y = log(I_ppfd), shape = site, color = depth_m, size = source)) +
    scale_color_manual(values = c("surf" = "grey","2" = "orange", "5" = "steelblue")) +
    scale_size_manual(values = c("BOM" = 1.5, "CRC" = 2.5)) +
    scale_shape_manual(values = c("Dover" = 1, "Triabunna" = 1, "Okehampton" = 0, "Tower Bay" = 2)) +
    geom_line(data = filter(y.I.CRC, kW.used == "other"), aes(x = day_t, y = log(val), linetype = depth)) +
    scale_linetype_manual(values = c("2m" = "solid", "5m" = "dashed")) +
    labs(x = "Day of the year", y = irr_lab) + nice
)
```

```{r final T plot}
(p.Temp <- ggplot(data = data.env) +
   geom_point(aes(x = day_t, y = temp.ave, shape = depth_m, color = site, size = source)) +
    scale_shape_manual(values = c("2" = 0, "5" = 0, "surf" = 1)) +
    scale_color_manual(values = c("Dover" = "grey", "Triabunna" = "grey", 
                                  "Okehampton" = "orange", "Tower Bay" = "steelblue")) +
    scale_size_manual(values = c("BOM" = 1.5, "CRC" = 2.5)) +
    geom_line(data = y.T.CRC, aes(x = day_t, y = Oke), linetype = "solid") +
    geom_line(data = y.T.CRC, aes(x = day_t, y = Tow), linetype = "dashed") +
    labs(y = temp_lab, x = "Day of the year") + nice)
```

```{r save I and T plots, eval = FALSE}
ggsave("outputs/final_I.png",
       p.Irr, # Name of plot
       width = 0.393701*23.87*0.75,
       height = 0.393701*10.41,
       unit = "in")

ggsave("outputs/final_T.png",
       p.Temp, # Name of plot
       width = 0.393701*23.87*0.75,
       height = 0.393701*10.41,
       unit = "in")
```

## Nutrients

### Swadling data

```{r load swadling data}
nitrogen <-
  read.csv("C:/Users/treimer/OneDrive - University of Tasmania/Other people's data/Swadling 2018/ECP_GEOSERVER_NUTRIENTS.csv",
               sep = ',')

nitrogen <- nitrogen %>%
  mutate(date = as.Date(as.data.frame(str_split_fixed(nitrogen$DATE_TRIP, "T", 2))[, 1]),
         month = month(date),
         year = year(date),
         trip = as.factor(TRIP_ID),
         site = as.factor(SITE_CODE),
         latitude = LATITUDE,
         longitude = LONGITUDE,
         depth = as.numeric(DEPTH),
         ammonium = as.numeric(AMMONIUM),
         nitrate = as.numeric(NITRATE_NITRITE),
         nitrite = as.numeric(NITRITE),
         nitrate = case_when(
           is.na(nitrite) | is.na(nitrate) ~ nitrate,
           TRUE ~ nitrate-nitrite)) %>%
  dplyr::select(date, month, year, site, latitude, longitude, depth, ammonium, nitrate, nitrite)

n.sites <- nitrogen %>%
  group_by(site) %>%
  dplyr::summarise(longitude = mean(longitude),
         latitude = mean(latitude))

# ggmap(get_stamenmap(bbox = c(min(n.sites$longitude)-0.25, # min long
#                      min(n.sites$latitude)-0.25, # min lat
#                      max(n.sites$longitude)+0.25, # max long
#                      max(n.sites$latitude)+0.25  # max lat
#                      ),
#   zoom = 10, maptype = "terrain-background")) +
#   theme_void() +
#   theme(panel.border = element_rect(colour = "grey", fill = NA, size = 2)) +
#   geom_point(data = n.sites, aes(y = latitude, x = longitude), size = 2)+
#   ggrepel::geom_text_repel(data = n.sites, aes(y = latitude, x = longitude,label=site))
```

Sites 3 and 4 are pretty far away from the rest. Exclude?

```{r initial N plot swadling}
n.surf <- nitrogen %>%
  filter(depth <= 50,
        # site != "SB4",
        # site != "SB3"
        ) %>%
  gather("chem", "val", ammonium, nitrate, factor_key = TRUE) %>% 
  mutate(ave.day = month * 30.345)

n.surf <- n.surf %>%
  group_by(ave.day, chem) %>%
  dplyr::summarise(val.m = mean(val),
                   val.se = std.error(val))

(p.init.N<-ggplot(n.surf, aes(x = ave.day, y = val.m, fill = chem, ymin = val.m + val.se, ymax = val.m - val.se)) +
    geom_col(position = position_dodge(width = 27.5)) +
    geom_errorbar(position = position_dodge(width = 27.5), width = 0.3*27.5))
```

### CRC-P data

```{r load crcp nutrient data}
n.CRC <-
  read.csv("C:/Users/treimer/OneDrive - University of Tasmania/Other people's data/CRC-P WP1 & 2 data/seawater_nutrients.csv", sep = ',')

n.CRC <- n.CRC %>%
  dplyr::select(Day, Month, Year, Name_site, Depth_m, NO3.NO2, NH4, Near_salmon, Longitude, Latitude)

n.CRC$Near_salmon[n.CRC$Name_site == "Tower Bay"] <- "Unk"

n.CRC <- n.CRC %>% 
  mutate(month = as.numeric(Month),
         year = as.numeric(Year),
         date = make_date(year, month, Day),
         site = as.factor(Name_site),
         depth = as.factor(Depth_m),
         nitrate = NO3.NO2,
         ammonium = NH4,
         near_sal = as.factor(Near_salmon)) %>% 
  dplyr::select(-Day,-Month,-Name_site,-Depth_m,-NO3.NO2,-NH4,-Near_salmon)

n.CRC$near_sal[n.CRC$site == "Tower Bay"] <- as.factor("Unk")
```

```{r initial N plot crcp}
n.data <- n.CRC %>%
  gather("chem", "val", ammonium,nitrate, factor_key = TRUE) %>% 
  mutate(ave.day = month * 30.345) %>%
  group_by(site, ave.day, chem, near_sal) %>%
  dplyr::summarise(
    val.m = mean(val),
    val.se = std.error(val))

(p.init.N <- ggplot(n.data, aes(x = ave.day, y = val.m, fill = chem, ymin = val.m + val.se, ymax = val.m - val.se)) +
    geom_col(position = position_dodge(width = 27.8)) +
    geom_errorbar(position = position_dodge(width = 27.8), width = 27.5*0.3) +
    facet_wrap(vars(site, near_sal), nrow = 2))
```

### Combining data

```{r combining nutrient data}
n.1 <- nitrogen %>%
  filter(depth <= 50) %>%
  mutate(near_sal = as.factor("Unk"),
         source = as.factor("swadling")) %>% 
  dplyr::select(-nitrite)

n.2 <- n.CRC %>%
  mutate(date = date) %>%
  mutate(month = as.numeric(month),
         year = as.numeric(Year),
         latitude = Latitude,
         longitude = Longitude) %>%
  relocate(date, .before = month) %>%
  relocate(near_sal, .after = nitrate) %>%
  relocate(latitude, .after = site) %>%
  relocate(longitude, .after = latitude) %>%
  relocate(ammonium, .before = nitrate) %>%
  mutate(source = as.factor("CRC")) %>%
  dplyr::select(-Year, -Longitude, -Latitude)
n.2$near_sal[n.2$near_sal=="Unk"] <- "Y"

n.all.long <- rbind(n.1, n.2) %>% 
  gather("chem", "val", ammonium, nitrate,  factor_key = TRUE) %>%
  mutate(ave.day = month * 30.345,
         val.umol.L = val,
         val.mgN.m3 = val * 14.0067) %>% 
  dplyr::select(-val)
  
n.all.sites <- n.all.long %>%
  group_by(site) %>%
  dplyr::summarise(longitude = mean(longitude),
                   latitude = mean(latitude))

n.all.short <- n.all.long %>%
  group_by(source, ave.day, chem, near_sal) %>%
  dplyr::summarise(m.umol.L = mean(val.umol.L, na.rm = TRUE),
                   umol.L.se = std.error(val.umol.L),
                   m.mgN.m3 = mean(val.mgN.m3),
                   mgN.m3.se = std.error(val.mgN.m3, na.rm = TRUE))

rm(n.1, n.2)
```

```{r initial plot all nutrients}
(p.all.N <- ggplot(n.all.short, aes(x = ave.day, y = m.umol.L, fill = near_sal, group = source, ymin = m.umol.L + umol.L.se, ymax = m.umol.L - umol.L.se)) +
   geom_col(position = position_dodge(width = 27.5)) +
   geom_errorbar(position = position_dodge(width = 27.5), width = 27.5*0.3) +
   facet_wrap(vars(chem), scales = "free_y") +
   theme_classic() +
   labs(x = "Day", y = "umol/L"))
```

It's pretty clear from the above facet chart that nitrate is pretty unaffected by whether or not salmon are nearby, but ammonium clearly is. I'm going to deal with them seperately, since they're so different.

```{r seperate by nutrient}
n.amm.long <- n.all.long %>%
  filter(chem == "ammonium")
n.amm.short <- n.amm.long %>%
  group_by(source, ave.day, near_sal) %>%
  dplyr::summarise(m.umol.L = mean(val.umol.L),
                   umol.L.se = std.error(val.umol.L),
                   m.mgN.m3 = mean(val.mgN.m3),
                   mgN.m3.se = std.error(val.mgN.m3))

n.nit.long <- n.all.long %>%
  filter(chem == "nitrate")
n.nit.short <- n.nit.long %>%
  group_by(source, ave.day) %>%
  dplyr::summarise(m.umol.L = mean(val.umol.L),
                   umol.L.se = std.error(val.umol.L),
                   m.mgN.m3 = mean(val.mgN.m3),
                   mgN.m3.se = std.error(val.mgN.m3))

(p.amm <- ggplot(n.amm.short, aes(x = ave.day, y = m.umol.L, ymin = m.umol.L + umol.L.se, ymax = m.umol.L - umol.L.se)) +
    geom_col(position = position_dodge(width = 27.5)) +
    geom_errorbar(position = position_dodge(width = 27.5), width = 0.3*27.5) +
    facet_wrap(vars(source)) +
    ggtitle("ammonium"))

(p.nit <- ggplot(n.nit.short, aes(x = ave.day, y = m.umol.L, fill = source, ymin = m.umol.L + umol.L.se, ymax = m.umol.L - umol.L.se)) +
    geom_col(position = position_dodge(width = 27.5)) +
    geom_errorbar(position = position_dodge(width = 27.5), width = 0.3*27.5) +
    ggtitle("nitrate"))

back.Am <- n.amm.short %>% 
  group_by(source) %>% 
  dplyr::summarise(mg.N = mean(m.mgN.m3, na.rm = TRUE),
                   umol.L = mean(m.umol.L, na.rm = TRUE))
```
### New forcing functions

It's pretty clear that the "background" ammonium should basically be constant.

```{r nls ammonium}
(back.amm.N <- mean(n.amm.long$val.mgN.m3[n.amm.long$source == "swadling"], na.rm = TRUE))

x.N <- as.formula(m.mgN.m3 ~ aN + sin((2 * pi * (ave.day + bN) + pi / 2) / 365) * cN)

y.N.amm <- nls(x.N, start = list(aN = 1, bN = 100, cN = 2), data = filter(n.amm.short, source == "CRC"))
summary(y.N.amm)
aN.amm <- 6 #round(coef(summary(y.N.amm))[1], 2)
bN.amm <- 190 #round(coef(summary(y.N.amm))[2], 0)
cN.amm <- 60 #round(coef(summary(y.N.amm))[3], 2)

n.amm.short$ave.day <- round(n.amm.short$ave.day)
year.amm <- merge(t, n.amm.short, by.x = "day_t", by.y = "ave.day", all.x = TRUE) 
year.amm <- year.amm %>% 
  mutate(f.amm = aN.amm + sin((2 * pi * (day_t + bN.amm) + pi / 2) / 365) * cN.amm,
         source = "CRC") %>% 
  mutate(f.amm2 = case_when(f.amm > back.amm.N ~ f.amm,
                            TRUE ~ back.amm.N)) %>% 
  pivot_longer(names_to = "method", values_to = "conc", cols = c(f.amm2, mgN.m3.se))

ggplot(data = year.amm, aes(x = day_t, y = conc, shape = method, color = near_sal)) +
    geom_point()
  #geom_errorbar(position = position_dodge(width = 2)) +
    #geom_line(aes(x = day_t, y = f.amm2))
```

```{r nls nitrate}
x.N <- as.formula(m.mgN.m3 ~ aN + sin((2 * pi * (ave.day + bN) + pi / 2) / 365) * cN)

y.N.nit <-
  nls(x.N,
      start = list(aN = 4, bN = 10, cN = 2),
      data = n.nit.short)

summary(y.N.nit)
(aN.nit <- round(coef(summary(y.N.nit))[1], 2))
(bN.nit <- round(coef(summary(y.N.nit))[2], 0))
(cN.nit <- round(coef(summary(y.N.nit))[3], 2))

mean(n.nit.short$m.mgN.m3[n.nit.short$source == "CRC"])
mean(n.nit.short$m.mgN.m3[n.nit.short$source == "swadling"], na.rm = TRUE)

t <- as.data.frame(seq(1:365))
colnames(t) <- "day_t"
n.nit.short$ave.day <- round(n.nit.short$ave.day, 0)
year.nit <- merge(t, n.nit.short, by.x = "day_t", by.y = "ave.day", all.x = TRUE) 
year.nit <- year.nit %>% 
  mutate(f.nit = (aN.nit*1.25 + sin((2 * pi * (day_t + bN.nit) + pi / 2) / 365) * cN.nit))
year.nit <- as.data.frame(year.nit)

(ggplot(data = year.nit, aes(x = day_t, y = m.mgN.m3, fill = source)) +
    geom_col(width = 50, position = position_dodge2(width = 0.8)) +
    geom_errorbar(aes(x = day_t,
                      ymin = m.mgN.m3 + mgN.m3.se,
                      ymax = m.mgN.m3 - mgN.m3.se),
                  position = position_dodge2(width = 0.8), width = 10) +
    geom_line(aes(x = day_t,
                  y = f.nit))) +
  theme_classic()

rm(y.N.nit)
```

## Final plots

```{r fianl ammonium plot}
(p.amm <- ggplot(data = n.amm.short, aes(x = ave.day, y = m.mgN.m3, 
                                         #ymin = m.mgN.m3 + mgN.m3.se, ymax = m.mgN.m3 - mgN.m3.se,
                                         # y = log(val.m) + 3, ymin = log(val.m + val.se) + 3, ymax = log(val.m - val.se) + 3,      
                                         fill = source)) +
    geom_col(alpha = 0.4, position = position_dodge(), width = 25, color = "black") +
    #geom_errorbar(width = 8, position = position_dodge(width = 25)) +
    geom_line(data = year.amm, aes(x = day_t, y = back.amm.N, linetype = "dashed")) +
    # scale_y_continuous(limits = c(0, 7), breaks = seq(0, 7, 0.5), labels = seq(-3, 4, 0.5)) +
    scale_fill_manual(values = c("CRC" = "red", "swadling" = "blue")) +
    theme_classic() +
    labs(x = "Day of the year", y = lab_amm) +
    theme(legend.position = "none"))
```

```{r final nitrate plot}
year.nit.2 <- year.nit %>% 
  dplyr::select(day_t, f.nit)

(p.nit <- ggplot(data = n.nit.short, 
                 aes(x = ave.day, y = m.umol.L), position = position_dodge()) +
   geom_col(aes(fill = source), alpha = 0.6, position = position_dodge2(), width = 25, color = "black") +
   geom_errorbar(aes(fill = source, ymin = m.umol.L + umol.L.se, ymax = m.umol.L - umol.L.se),
                 width = 8, position = position_dodge(width = 25)) +
   geom_line(data = year.nit.2, aes(x = day_t, y = f.nit/14.0067)) +
   nice + prettybars + labs(x = "Day of the year", y = lab_nit))
```

```{r save nutrient plots, eval = FALSE}
ggsave("outputs/figures/final_nit.png",
  p.nit, # Name of plot
  width = 0.393701*23.87*0.75,
  height = 0.393701*10.41,
  unit = "in")
```


